Using DIT to simplify the DBF feasibility test

### 2013-07-19 dit-paper.tex

Starting from the definition, it remains to find a method to compute the values
of $h_i(0, t)$ (noted $h_i(t)$ from now on). In the synchronous case, these
values can be obtained as $$h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
k T_i  + D_i \leq t \} + 1 $$ Indeed, $k = 0$ correspond to the first task, $k =
1$ to the second task, etc. The maximal value of $k$ can be explicitly stated by rearranging the condition:
$$k T_i + D_i \leq t$$
$$\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor$$
The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$. If this value is negative, it means that no job of task $\tau_i$ respects the condition, i.e. $h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\

@@

In \cite{baruah1990algorithms}, the authors show that the DBF can be used to derive the following feasibility condition for EDF\footnote{And thus, EDF being optimal, for all optimal schedulers} on sporadic task sets. An adapted proof is given here.

>>>>

Starting from the definition, it remains to find a method to compute the values
of $h_i(0, t)$ (noted $h_i(t)$ from now on). In the synchronous case, these
values can be obtained as 
\[
	h_i(t) = \operatorname{max} \; \{ k \in \mathbb{N} :
	k T_i  + D_i \leq t \} + 1
\]
Indeed, $k = 0$ correspond to the first task, $k = 1$ to the second task, etc.
The maximal value of $k$ can be explicitly stated by rearranging the condition:
\[
	\begin{array}{c}
		k T_i + D_i \leq t \\
		\iff 0 \leq k \leq \lfloor \frac{t - D_i}{T_i} \rfloor
	\end{array}
\]
The highest value is $k = \lfloor \frac{t - D_i}{T_i} \rfloor$. If this value is
negative, it means that no job of task $\tau_i$ respects the condition, i.e.
$h_i(t) = 0$. Else, we can inject it directly and obtain $h_i(t) = \lfloor \frac{t - D_i}{T_i} \rfloor + 1$\\

@@

In \cite{baruah1990algorithms} it is shown that the DBF can be used to
derive the following feasibility condition for EDF (and thus, EDF being
optimal, for all other optimal schedulers) on sporadic task sets. An adapted
proof is given here.
